\documentclass[11pt,a4paper]{article}

% -------------------- PACKAGES --------------------
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{setspace}

% -------------------- FORMATTING --------------------
\setstretch{1.1}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\pagenumbering{gobble}

% -------------------- DOCUMENT --------------------
\begin{document}

\begin{center}
    {\LARGE \textbf{Antony K. Cheruiyot}}\\
    \vspace{4pt}
    \href{mailto:tonyneon2020@gmail.com}{tonyneon2020@gmail.com} \;\; \\
    +254 705 826 009 / +90 533 844 0474\\
\end{center}

% -------------------- PROFILE --------------------
\section*{Professional Profile}
Detail oriented and motivated engineering student with a strong foundation in electrical engineering and software engineering. Experienced in industrial maintenance, equipment monitoring, and technical documentation. Demonstrates leadership through student governance and community representation. Adept at problem-solving, teamwork, and applying engineering principles in practical environments.

% -------------------- CAREER OBJECTIVE --------------------
\section*{Career Objective}
To grow into a versatile engineering professional with competencies in electrical systems, software engineering, automation, and industrial maintenance, capable of diagnosing problems, implementing sustainable solutions, and contributing to organizational efficiency while upholding ethical and environmental standards.

% -------------------- EDUCATION --------------------
\section*{Education}

\textbf{Bachelor of Science in Software Engineering} \\
European University of Lefke (EUL), Cyprus \\
2024 -- Present

\vspace{6pt}

\textbf{Diploma in Electrical Engineering} \\
Kiambu Institute of Science and Technology, Kenya \\
September 2020 -- Present

\vspace{6pt}

\textbf{Kenya Certificate of Secondary Education (KCSE)} \\
Naivasha Boys High School, Kenya \\
January 2016 -- November 2019

% -------------------- EXPERIENCE --------------------
\section*{Work Experience}

\textbf{Industrial Attachment – Electrical Engineering Trainee} \\
Royal Steel Mills Company, Kenya \\
January 2022 -- March 2022

\begin{itemize}[leftmargin=*]
    \item Monitored industrial electrical and mechanical equipment to detect abnormalities and prevent failures.
    \item Assisted in preventive and corrective maintenance activities across production systems.
    \item Participated in root cause analysis of equipment breakdowns and documented findings in maintenance reports.
    \item Ensured accurate completion of maintenance logs and technical documentation.
\end{itemize}

% -------------------- PROJECTS --------------------
\section*{Technical Projects}

\textbf{CityDrive – Full-Stack Automotive Gallery} \hfill \href{https://github.com/Ruchez/citydrive}{GitHub} \\
Lead Developer \\
\begin{itemize}[leftmargin=*]
    \item Engineered a premium web application for vehicle inventory management using \textbf{React}, \textbf{TypeScript}, and \textbf{Supabase}.
    \item Designed a "Museum-Grade" UI following the \textbf{Simplicity 4.0} aesthetic, featuring immersive responsive hero framing and glassmorphism.
    \item Developed a high-performance admin dashboard with real-time stats, secure authentication, and architectural navigation.
    \item Optimized frontend performance through lazy loading and responsive image switching for a "perfect fit" across all devices.
\end{itemize}

% -------------------- LEADERSHIP --------------------
\section*{Leadership Experience}

\textbf{President, Kenyan Community} \\
European University of Lefke (EUL) \\
2024 -- Present

\begin{itemize}[leftmargin=*]
    \item Represent Kenyan students in academic and social affairs within the university.
    \item Coordinate cultural, academic, and welfare activities for community members.
    \item Serve as a liaison between students and university administration.
\end{itemize}

% -------------------- SKILLS --------------------
\section*{Technical Skills}

\begin{itemize}[leftmargin=*]
    \item \textbf{Software:} React, TypeScript, Supabase, Git, PostgreSQL, Frontend UI/UX
    \item \textbf{Electrical:} Installation, Maintenance, Industrial Equipment Monitoring
    \item \textbf{General:} Root Cause Analysis, Technical Documentation, Safety Compliance
\end{itemize}

% -------------------- SOFT SKILLS --------------------
\section*{Soft Skills}

\begin{itemize}[leftmargin=*]
    \item Problem Solving, Leadership, Team Coordination, Communication, Adaptability
\end{itemize}

% -------------------- REFERENCES --------------------
\section*{References}
Available upon request.

\end{document}
